\documentclass[a4paper]{my_cv}
\begin{document}

%\addtolength{\bottommargin}{-5cm}
\thispagestyle{empty}	
\pageheader{Artur~}{Benevides}
	{+55 21 96543 5755}
 	{\href{mailto:benevidesartur@gmail.com}{benevidesartur@\\gmail.com}}
	{ \href{https://github.com/arturbenevides}{/arturbenevides}} 	
 	{ \href{https://www.linkedin.com/in/artur-benevides-5272b4b3}{/in/artur-benevides-5272b4b3}}
	{ General Bruce, 72, Rio de Janeiro }
	{21.02.1990}
	
		
% TODO
% izvali kako da promenis font na neki koji je kul (pogledaj ove tempate?) DONE
% ubaci fotku onu sa strane (vidi kako je u template i da li tikz moze to da uradi) DONE
% izvali kako da podesis kolonu sa strane gde mozes da stavljas stvari (opet, vidi template) DONE
% vidi kako se ukljucuju progress barovi DONE
% vidi kako u sekciji za obrazovanje da ga nateras da bude minimalne sirine te i te
% itd (nadji jos kul ideja)

 
\begin{aside}
\section{Languages}
~
% 3 is max
\bodyfont\skills{{Portuguese/3}, {English/1.8}, {German/0.7}}
~
~
\section{Programming}
% 3 is max
~
\skills{ {HTML/.7},{Ruby on Rails/0.7},{Markdown/2.3},{LaTeX/3},{GNU Linux/2},{Git/2},{MATLAB/1},{FORTRAN/1.8},{Python/2}}
~
~
\section{Interests}
%3 is max
~
\bodyfont\skills{{Programming/3},{Geophysics/3},{Geology/3}, {Physics/3}, {Mathematics/3}}

\end {aside}
~
~\\
\section{Education}
\begin{entrylist}
  \entry
    {2017~\textemdash \\ present}
    {Master's Degree in Applied Geophysics}
    {National Observatory, ON-MCTIC (RJ, Brazil)}
    {Research project: 3D Magnetotelluric Imaging of the Iguatu Basin: hydrogeological implications (Grantee of CNPq)\\ Advisor: Sergio Fontes}
  \entry
    {2012~\textemdash \\2016}
    {Bachelor's Degree in Geophysics}
    {Federal University of Bahia - UFBA (BA, Brazil)}
    {Title: Inversion of BHT for Determinig Geothermal Gradient (Grantee of FAPESB)\\
     Advisor: Amin Bassrei}

\end{entrylist}

\section{Experience}
\begin{entrylist}
	\entry
	{2014~\textemdash \\2017}
	{Internship}
	{Laboratory of Petroleum Exploration | LAGEP - UFBA}
	{Scientific initiation scholarship, 20h (weekly), schemes of job: part-time}
	\entry
	{2016~\textemdash \\2016}
	{Physics teacher}
	{CPM - Dendezeiros, Salvador (BA, Brazil)}
	{Internship as substitute teacher in high school}
	\entry	
	{2007~\textemdash \\2008}
	{Internship}
	{State University of Southwest Bahia, Jequié (BA, Brazil)}
	{Collaborating in the audiovisual sector}
\end{entrylist}

\section{Projects}
\setlength{\tabcolsep}{15pt}
\begin{tabularx}{1.07\textwidth}{XXX}
	\textbf{3D inversion of MT data:} inversion of impedance tensor using algorithm NLGG (ModEM) &
	\textbf{Vassouras Magnetic Observatory (VSS):} we evaluate the possible occurrences of Geomagnetics Jerks\\
	\textbf{Regularization:} an implementation of the regularization to inversion parameters
	\textbf{} \\
\end{tabularx}
~
\section{Bibliographical Production }
\bodyfont

\begin{aplist}
	
	\apentry{}{\textbf{Benevides A., Camacho E., Silveira V., Melhorato R., Rodrigo I. \& Pinheiro K.}, 2017. One Century of data from Vassouras Magnetic Observatory (1915-2015). II PANGEO (Vassouras - RJ) Poster}
	\apentry{}{\textbf{Benevides A.}, 2016. Processing and application of Bottom-Hole Tempreature (BHT) Data. I Week of Non-seismics Methods. (Salvador - BA). Talk presentation}
	\apentry{}{\textbf{Benevides A. \& Bassrei A.}, 2016. Inversion of BHT for Determinig Geothermal Gradient: Aplication to Pineview Data (Utah, US). VII SimBGf (Ouro Preto - MG) Poster}
	

\end{aplist}


\section{Other Relevant Information}
\bodyfont

\begin{aplist}
\apentry{}{Organizing committee of the V, VI and VI week of geophysics - UFBA}
\apentry{}{Brazillian Geophysical Society, member since 2012}
\apentry{}{UFBA Student Chapter - EAGE, member in 2016 (1st in World Geoquiz Online)}
\textit\footnotesize{All the bibliographical production and other projects are free in my GitHub profile linked above}
\end{aplist}

\end{document} 